### 2021-12-12 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_networkary_classifiers@7cc292d1076ac679f470425645eb6e4e1eaaac37 🚀

\begin{figure}
\hypertarget{fig:connectance}{%
\centering
\includegraphics{figures/changing-connectance.png}
\caption{TODO}\label{fig:connectance}
}
\end{figure}

These two analyses point to the following recommendations: MCC is indeed
more appropriate than \(\kappa\), as although sensitive to bias, it is
sensitive in a consistent way. Informedness is appropriate at
discriminating between different skills, but confounded by bias. \(F_1\)
is increasing with bias, and should not be prioritized to evalue the
performance of the model. The discussion of sensitivity to bias should
come with a domain-specific caveat: although it is likely that
interactions documented in ecological networks are correct, a lot of
non-interactions are simply unobserved; as predictive models are used
for data-inflation (\emph{i.e.} the prediction of new interactions), it
is not necessarilly a bad thing to select models that predict more
interactions than the original dataset, because the original dataset
misses some interactions.

>>>>

\begin{figure}
\hypertarget{fig:connectance}{%
\centering
\includegraphics{figures/changing-connectance.png}
\caption{As in fig.~\ref{fig:bias}, consequences of changing connectance
for different levels of classifier skill, assuming no classifier bias.
Informedness, \(\kappa\), and MCC do increase with connectance, but only
when the classifier is not no-skill; by way of contrast, a more
connected network will give a higher \(F_1\) value even with a no-skill
classifier.}\label{fig:connectance}
}
\end{figure}

These two analyses point to the following recommendations: MCC is indeed
more appropriate than \(\kappa\), as although sensitive to bias, it is
sensitive in a consistent way. Informedness is appropriate at
discriminating between different skills, but confounded by bias. \(F_1\)
is increasing with bias, and should not be prioritized to evalue the
performance of the model. The discussion of sensitivity to bias should
come with a domain-specific caveat: although it is likely that
interactions documented in ecological networks are correct, a lot of
non-interactions are simply unobserved; as predictive models are used
for data-inflation (\emph{i.e.} the prediction of new interactions), it
is not necessarilly a bad thing in practice to select models that
predict more interactions than the original dataset, because the
original dataset misses some interactions. Furthermore, the weight of
positive interactions could be adjusted if some information about the
extent of undersampling exists (\emph{e.g.} Branco et al., 2015).
